### 2017-09-06 Documents/bootcamp_3ideas.tex
Intro outline, 3 ideas modified

\begin{document}
\bigskip
\centerline{\Large \bf Data Bootcamp: Three Project Ideas}
\medskip
\centerline{Revised: \today}

>>>>

\begin{document}

\centerline{\Large \bf Thinking about data}
\bigskip

\begin{itemize}

\item Data + Picture = a compelling way to tell a story

\item Where we're headed
\begin{itemize}
\item Think of a {\bf graph\/} you'd like to produce -- a ``visualization''
\item And the {\bf story\/} it tells
\item And the {\bf data\/} that went into it
\end{itemize}

\item Examples (links on {\it Topic outlines \& links\/} page) [Gapminder]

\item Questions about graphs
\begin{itemize}
\item What did you learn, what is the {\bf story\/}?
\item {\bf What else} would you like to know?
\item Where did the {\bf data\/} come from?
\end{itemize}

\item Examples revisited, answer the questions

\item Course projects
\begin{itemize}
\item Course structure:  tools, project
\item Opportunity to show off your skills (Projects directory of GitHub repo)
\item First step:  develop project ideas ({\bf ideas are developed, not discovered})
\item What interests {you}? (finance? movies?  soccer?)
\end{itemize}

\item Idea machines
\begin{itemize}
\item Start with an idea or subject (what interests you?)
\item Start with a dataset (you'll know more shortly)
\item Start with an example (see link on data page)
\item Start with a suggestion from the people you work with
\end{itemize}

\item Three ideas
\begin{itemize}
\item Put red sticker on your computer
\item Goal:  write down three ideas, 1-2 sentences each (see handout)
\item Use your imagination, don't overthink it (improv: what's your name?)
\item Talk to your neighbors, bounce ideas around
\item Or look at the {\it Data sources\/} page of the course website
\item When you're done, switch to green sticker
\item Share an idea with the class, ask for suggestions for developing further
\item Save ideas for future reference
\item Optional:  leave a copy with me
\end{itemize}
\end{itemize}

\newpage

\bigskip
\centerline{\Large \bf Data Bootcamp: Three Project Ideas}

### 2017-09-06 Documents/bootcamp_topic_intro.tex
Intro outline, 3 ideas modified

\begin{itemize}
\item  First-day handouts:  Syllabus, Project Guide, Due Dates
\item  Today's handouts:  this outline, three ideas (two copies), book chapters, red/green stickers
\item  All posted on website (except the stickers).
\end{itemize}

@@

\section*{\href{https://atom.io/}{Atom}}
\begin{itemize}
\item A versatile, text editor. Must have tool for serious work.
\item We will use it to open files, look at them, learn some markdown.
\item Lets install it
\begin{itemize}
\item Put red sticker on your laptop
\item Google ``atom download'' or borrow a USB drive
\item Download or copy installer to your computer
\item Run installer
\item Start Atom
\item Replace red sticker with green when Atom opens
\end{itemize}
\item Go and open new file
\item type my first file, then comma, then birth year, then comma, high school graduation year, then comma, college graduation year (or expected graduation year). For me it is like this\\
    \\
{\tt my first file, 1978, 1996, 2001} 
\item Save as {\tt my-first-file.csv} in your \verb|Data_Bootcamp| file.
\item \textbf{Pro-tip: naming convention and file type is important in this course}
\end{itemize}

\section*{\href{https://github.com}{GitHub}}
\begin{itemize}
\item What I will use it for\ldots
\begin{itemize}
\item Source of ALL course materials
\item Place for you to grab materials on the fly. Save files by cut and paste, clever save as, or "Raw" (ask about this)
\end{itemize}
\item You need to create an account and email me your username
\item What you will use it for\ldots
\begin{itemize}
\item Post your homework and projects; I will ``pull'' them from there.
\item Long run: Think of this like an artists portfolio. Here you can post your code and projects and show potential employers, family, friends what you have done.
\end{itemize}
\item Now lets use it
\begin{itemize}
\item Create a new repository and name it {\tt my-first-repository},
\item place the {\tt my first file.csv} file you created in it,
\item Great job! Next class, I'm going to try and ``pull'' the file and then report some statistics about the class to you.
\end{itemize}
\end{itemize}

@@

\needspace{2\baselineskip}
\item Run test program in Spyder
\begin{itemize}
\item Put red sticker on your laptop
\item From Launcher, launch Spyder (labelled ``spyder-app'')
\item Look around (editor, IPython console, Object inspector)
\item Enter test program in editor (on the left)
\item Save in \verb|Data_Bootcamp| directory as \verb|bootcamp_test.py|
(File, Save as, look for folder)
\item Run program (click on large green triangle)
\item Look for correct output (last line should be {\tt 3.5.x etc})
\item Switch to green sticker if it works
\end{itemize}

@@

\begin{center}
\begin{tabular}{cc}
\toprule
Environment & File or Object \\
\midrule
MS Word  & Word document  \\
 & Excel file     \\
iTunes & \\
%Typewriter & \\
Spyder   &                \\
\bottomrule
\end{tabular}
\end{center}

@@

\item {\it Only if you have time.\/} Try this program: \verb|OECD_health_indicators.py|.
What do you see?  What questions does it raise?
(There are other files in the same directory, but some of them don't work yet.)
\end{enumerate}

\section*{Thinking about data}

\begin{itemize}

\item Data + Picture = a compelling way to tell a story

\item Where we're headed
\begin{itemize}
\item Think of a {\bf graph\/} you'd like to produce -- a ``visualization''
\item And the {\bf story\/} it tells
\item And the {\bf data\/} that went into it
\end{itemize}

\item Examples (links on {\it Topic outlines \& links\/} page) [Gapminder]

\item Questions about graphs
\begin{itemize}
\item What did you learn, what is the {\bf story\/}?
\item {\bf What else} would you like to know?
\item Where did the {\bf data\/} come from?
\end{itemize}

\item Examples revisited, answer the questions

\item Course projects
\begin{itemize}
\item Course structure:  tools, project
\item Opportunity to show off your skills (Projects directory of GitHub repo)
\item First step:  develop project ideas ({\bf ideas are developed, not discovered})
\item What interests {you}? (finance? movies?  soccer?)
\end{itemize}

\item Idea machines
\begin{itemize}
\item Start with an idea or subject (what interests you?)
\item Start with a dataset (you'll know more shortly)
\item Start with an example (see link on data page)
\item Start with a suggestion from the people you work with
\end{itemize}

\item Three ideas
\begin{itemize}
\item Put red sticker on your computer
\item Goal:  write down three ideas, 1-2 sentences each (see handout)
\item Use your imagination, don't overthink it (improv: what's your name?)
\item Talk to your neighbors, bounce ideas around
\item Or look at the {\it Data sources\/} page of the course website
\item When you're done, switch to green sticker
\item Share an idea with the class, ask for suggestions for developing further
\item Save ideas for future reference
\item Optional:  leave a copy with me
\end{itemize}
\end{itemize}

@@

\begin{itemize}
\item Required
\begin{itemize}
\item Read Syllabus and Project Guide.
\item Mark Due Dates on your calendar.
\item Skim chapters 1-3 of the book.
\end{itemize}
\item Recommended
\begin{itemize}
\item If you haven't already:  join the discussion group, take the entry poll.
\item Explore the website.  Make sure you can find the book, due dates,
topic outlines, assignments, and data sources.
\item Post a link to an interesting graph on the discussion group.
\item Look through the IPython notebook \verb|bootcamp_examples.ipynb|
in the {\tt Code/IPython} directory of the GitHub repo.
What graphs interest you?  What data?
Do they suggest anything else you might explore?
\end{itemize}
\end{itemize}

>>>>

\begin{itemize}
\item  Today's handouts:  Syllabus, due dates, this outline, red/green stickers
\item  All posted on website (except the stickers).
\end{itemize}

@@

\section*{\href{https://atom.io/}{Atom}}
\begin{itemize}
\item A versatile, text editor. Must have tool for serious work.
\item We will use it to open files, look at them, learn some markdown.
\item Lets install it
\begin{itemize}
\item Put red sticker on your laptop
\item Google ``atom download'' or borrow a USB drive
\item Download or copy installer to your computer
\item Run installer
\item Start Atom
\item Replace red sticker with green when Atom opens
\end{itemize}
\item Go and open new file
\item type my first file, then comma, then birth year, then comma, high school graduation year, then comma, college graduation year (or expected graduation year). For me it is like this\\
    \\
{\tt my first file, 1978, 1996, 2001} 
\item Save as: \verb|my-first-file.csv| in your \verb|Data_Bootcamp| file.
\item \textbf{Pro-tip: naming convention and file type is important in this course}
\end{itemize}

\section*{\href{https://github.com}{GitHub}}
\begin{itemize}
\item What I will use it for\ldots
\begin{itemize}
\item Source of ALL course materials
\item Place for you to grab materials on the fly. Save files by cut and paste, clever save as, or "Raw" (ask about this)
\end{itemize}
\item You need to create an account and email me your username
\item What you will use it for\ldots
\begin{itemize}
\item Post your homework and projects; I will ``pull'' them from there.
\item Long run: Think of this like an artists portfolio. Here you can post your code and projects and show potential employers, family, friends what you have done.
\end{itemize}
\item Now lets use it
\begin{itemize}
\item Create a new repository and name it {\tt my-first-repository},
\item place the \verb|my-first-file.csv| file you created in it,
\item Great job! Next class, I'm going to try and ``pull'' the file and then report some statistics about the class to you.
\end{itemize}
\end{itemize}

@@

\needspace{2\baselineskip}
\item Run test program in Spyder
\begin{itemize}
\item Put red sticker on your laptop
\item From Launcher, launch Spyder (labelled ``spyder-app'')
\item Look around (editor, IPython console, Object inspector)
\item Enter test program in editor (on the left)
\item Save in \verb|Data_Bootcamp| directory as \verb|bootcamp_test.py|
(File, Save as, look for folder)
\item Run program (click on large green triangle)
\item Look for correct output (last line should be {\tt 3.6.x etc})
\item Switch to green sticker if it works
\end{itemize}

@@

\begin{center}
\begin{tabular}{cc}
\toprule
Environment & File or Object \\
\midrule
MS Word  & Word document  \\
 & Excel file     \\
iTunes & \\
%Typewriter & \\
Atom & \\
Spyder   &                \\
\bottomrule
\end{tabular}
\end{center}

\item Open Atom and a new file. 
\begin{itemize}
\item In a similar fashion as above, create a {\tt .csv } file with the following information separated by commas
\begin{itemize}
\item Expected major (or concentration)
\item Scale of 1-5 (5 being a lot, 1 being none) experience with programming
\item preferred form of social media
\item career path (e.g. Finance, Consulting, Technology, Fashion, public policy, rock star)
\end{itemize}
\item Name as \verb|my-second-file.csv| and post on GitHub in {\tt my-first-repository}
\end{itemize}

@@

\item {\it Only if you have time.\/} Try this program: \verb|OECD_health_indicators.py|.
What do you see?  What questions does it raise?
(There are other files in the same directory, but some of them don't work yet.)

\end{enumerate}

@@

\begin{itemize}
\item Required
\begin{itemize}
\item Read Syllabus and Project Guide.
\item Mark Due Dates on your calendar.
\item Skim chapters 1-3 of the book.
\end{itemize}
\item Recommended
\begin{itemize}
\item If you haven't already:  join the discussion group.
\item Explore the website.  Make sure you can find the book, due dates,
topic outlines, assignments, and data sources.
\item Post a link to an interesting graph on the discussion group.
\item Look through the IPython notebook \verb|bootcamp_examples.ipynb|
in the {\tt Code/IPython} directory of the GitHub repo.
What graphs interest you?  What data?
Do they suggest anything else you might explore?
\end{itemize}
\end{itemize}
